<small> Supplementary materials for the main submission entitled - <br><br> Clustering time series based on probability distributions across temporal granularities

### 2021-11-07 main.Rmd
parcoord-sim parcoord in validation section, scenario (a), (b) and (c) changed to S1, S2 and S3

The proposed methods could be extended when two granularities of interest interact and we want to group subjects based on the interaction of the two granularities. Consider a group that has a different weekday and weekend behavior in the summer but not in the winter. This type of combined behavior across granularities can be discovered by evaluating the distribution across combinations of categories for different interacting granularities (Weekend/Weekday and month-of-year in this example). As a result, in this scenario, we analyze a combination of categories generated from different distributions. Consider a case in which there are only two interacting granularities of interest, $g1$ and $g2$. In contrast to the previous situation, when we could study distributions across $n_{g_1} + n_{g_2} = 5$ separate categories, with interaction, we must evaluate the distribution of the $n_{g_1}*n_{g_2}=6$ combination of categories. Consider the $4$ designs in Figure \ref{fig:interaction-gran}, where various distributions are assumed for different combinations of categories, resulting in different designs. Design $D1$ exhibits no change in distributions across $g1$ or $g2$, whereas Designs $D2$ and $D3$ alter across only $g1$ and $g2$, respectively. D4 varies across both $g1$ and $g2$ categories. D3 and D4 appear similar based on their relative differences across consecutive categories, but $D4$ also changes across facets, unlike $D3$, which has all facets look the same.

```{r interaction-gran, fig.cap = "Distribution of the simulated variable across $g1$ conditional on $g2$ is shown through boxplots for 4 designs. D1 has no change in distributions across different categories of $g1$ or $g2$, while D2 and D3 change across only $g1$ and $g2$ respectively. D4 changes across categories of both $g1$ and $g2$."}

@@

```{r parcoord-sim, fig.cap = "The parallel coordinate plot illustrates the total inter-cluster distances for granularities $g1$, $g2$, and $g3$. One line in the figure depicts the inter-cluster distances for a single simulation scenario. While the first plot indicates that no variable stands out during clustering, the next two designs demonstrate that g1 and (g1, g2) have relatively lower inter-cluster distances, indicating that they did not contribute to clustering. It is worth emphasising that these facts are consistent with our initial assumptions when designing the scenarios and (a), (b), and (c) correspond to Scenario (a), (b) and (c) respectively."}

>>>>

The proposed methods could be extended when two granularities of interest interact and we want to group subjects based on the interaction of the two granularities. Consider a group that has a different weekday and weekend behavior in the summer but not in the winter. This type of combined behavior across granularities can be discovered by evaluating the distribution across combinations of categories for different interacting granularities (Weekend/Weekday and month-of-year in this example). As a result, in this scenario, we analyze a combination of categories generated from different distributions. Display of design and related results can be found in supplementary.

@@

```{r parcoord-sim, fig.cap = "The parallel coordinate plot illustrates the total inter-cluster distances for granularities $g1$, $g2$, and $g3$. One line in the figure depicts the inter-cluster distances for a single simulation scenario. While the first plot indicates that no variable stands out during clustering, the next two designs demonstrate that g1 and (g1, g2) have relatively lower inter-cluster distances, indicating that they did not contribute to clustering. It is worth emphasising that these facts are consistent with our initial assumptions when designing the scenarios and S1, S2, S3 correspond to scenarios with three, two and one significant granularity respectively."}

### 2021-11-07 paper-supplementary.Rmd
parcoord-sim parcoord in validation section, scenario (a), (b) and (c) changed to S1, S2 and S3

>>>>

### Interaction of granularities

Consider a case in which there are only two interacting granularities of interest, $g1$ and $g2$. In contrast to the previous situation, when we could study distributions across $n_{g_1} + n_{g_2} = 5$ separate categories, with interaction, we must evaluate the distribution of the $n_{g_1}*n_{g_2}=6$ combination of categories. Consider the $4$ designs in Figure \ref{fig:interaction-gran}, where various distributions are assumed for different combinations of categories, resulting in different designs. Design $D1$ exhibits no change in distributions across $g1$ or $g2$, whereas Designs $D2$ and $D3$ alter across only $g1$ and $g2$, respectively. D4 varies across both $g1$ and $g2$ categories. D3 and D4 appear similar based on their relative differences across consecutive categories, but $D4$ also changes across facets, unlike $D3$, which has all facets look the same.

```{r interaction-gran, fig.cap = "Distribution of the simulated variable across $g1$ conditional on $g2$ is shown through boxplots for 4 designs. D1 has no change in distributions across different categories of $g1$ or $g2$, while D2 and D3 change across only $g1$ and $g2$ respectively. D4 changes across categories of both $g1$ and $g2$."}
